Why does female meiosis allow the opportunity for exploitation by selfish sperm? BETTER TITLE?

### 2013-09-20 writeup_and_notes/male_dependent_drive.tex
small changes to discussion

Finally given a system of a balanced meiotic drive system which avoid
its own ill effects through a sperm-based mechanism
, such as that depicted in Figure XX and XX, female-based modifiers 
can evolve that act to further facilitate the sperms action in
disrupting driver.

This logic may not hold for sex chromosomes. In ZW systems 
 Male modification of recombination rates
POssibility that this could happen in plants if pollen emit signals to ``egg''
Discussion of OM and IN.

>>>>

XY systems don't care. ZW systems (males ZZ, females ZW). If there is
sex ratio distortion how could this play out?

Finally given a system of a balanced meiotic drive system which avoid
its own ill effects through a sperm-based mechanism
, such as that depicted in Figure XX and XX, female-based modifiers 
can evolve that act to further facilitate the sperm's action in
disrupting driver.

 Male modification of recombination rates
POssibility that this could happen in plants if pollen emit signals to ``egg''
Discussion of OM and IN.
